### 2011-09-14 Text/paper.tex
Fighting with the codes. Still don't know what is the real number

@@

>>>>

\subsection{Average concentration}
As far as we used the inlet/outlet concentration in the expression of the calculation of the
volumetric mass transfer coefficient. However, the bubble in simulations located closely to the
inlet and with periodic boundary conditions that can change the volumetric mass transfer
coefficient significantly. As it will be discussed later in the appendix section, the assumption of
the periodic boundary conditions requires the continuous picture. The continuous picture requires as
well the average concentration to be of constant value. If the average concentration is used for
the calculation of the volumetric mass transfer coefficient {\color{red} (which can be more
adequate)}, then the volumetric mass transfer coefficient is more close to the correlation values,
see Fig. \ref{fig:average:concentration}. 
\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/steady_state_average.eps}
\caption{The calculation of the volumetric mass transfer coefficient, if instead the inlet/outlet
concentration the average concentration is used.\label{fig:average:concentration}}
\end{figure}
One can see that the average concentration requires more than 2 millions time iterations to come to
the steady-state.

@@

\section{Grid Refinement}
We performed a grid refinement study and compared it with the original data. For this purpose we
doubled every fluid node and ran simulations. One can see {\color{red} That's what I have at the
moment - need to write parallel version for the grid refinement} in Fig. \ref{fig:grid:comparison}
the comparison between original size and refined grid simulations data. The results are close,
especially it's important for larger velocities, where diffusion layer is underresolved.
\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/steady_state_comparison_grid.eps}
\caption{Comparison between the usual and refined grid simulations. One
can see that curves are close.\label{fig:grid:comparison}}
\end{figure}
